---
title: "Spatial Allocation with Perimiter Minimization"
author: "John Withrow, PhD"
date: "November 1, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Executive Summary



## Analytical Context
### Session Information
```{r sessionInfo}
sessionInfo()
```
### Setting of Random Number Seed
```{r rnd}
set.seed(19690828)
```
### Set Working Directory
```{r setwd}
setwd("C:\\Users\\John\\Documents\\SpatialAllocationWithPerimeterMinimization")
```

***

## Analytical Process
### Data Acquisition
Training and testing data are already divided into two files, downloadable from two different sources:


### Manual Pre-Processing
In both downloaded files, the title of the first column is missing.  It was added as "num" for both files, as it appears in both to be a simple enumeration column.

### Reading and Pre-processing of Data
The following pre-processing of data took place:
1. All columns after the seventh and before the last were set to type numeric
2. It was found that any column that had missing data had at most a few hundred records without missing data (out of over 13,000 total records).  These fields were removed from the study, reducing the total number of columns from 154 to 60.
```{r data}
m <- 1000
n <- 1000
pop <- matrix(data=0,nrow=m,ncol=n)
occ <- matrix(data=0,nrow=m,ncol=n)
bound <- matrix(data=0,nrow=(m+1)*(n+1),ncol=p)
s <- sample(seq(1,m*n))
row <- function(x,m) {x %/% m}
col <- function(x,m) {x %% m}
flip <- function(x,m) {bound[row(x,m),col(x,m)] <- (bound[row(x,m),col(x,m)]+1) %% 2}
occupy <- function(x,m,i)
{
  occ[row(x,m),col(x,m)] = i
  flip(bound[row(x,m),col(x,m)])
  flip(bound[row(x,m),col(x,m)+1])
  flip(bound[row(x,m)+1,col(x,m)])
  flip(bound[row(x,m)+1,col(x,m)+1])
}
isAdjacent <- function(x1,x2,m)
```

### Dimensionality Reduction


***

#### End of Analysis